---
title: "Hershey Font Format"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hershey-font-format}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hershey)
library(ggplot2)
```


## JHF - Hershey Font File format

The Hershey Font File format (.jhf) is a text file with encodings for all
the glyphs in the font.

The text is hard-wrapped at 72 characters-per-line, so longer glyphs get split 
across multiple lines.


## Glyph Encoding

The following is from [Paul Bourke's dataformats page](http://paulbourke.net/dataformats/hershey/).

The structure is basically as follows: 

| Position | Interpretation                               |
|----------|----------------------------------------------|
| 0-4      | Identifier (integer) - not unique!           |
| 5-7      | Number of vertices (integer)                 |
| 8        | Left position                                |
| 9        | Right position                               |
| ...      | Every pair of characters represents a vertex |

All vertex coordinates are given as a pair of characters.  The numeric value of
each vertex its ASCII value relative to the ASCII value of 'R'. 

The vertex coordinate of " R" indicates a *pen up* operation i.e. the drawing pen moves to the 
next location, but does not draw a stroke.

As an example consider the glyph:  `    8  9MWOMOV RUMUV ROQUQ`

* ID = 8
* Number of vertices = 9 - this means there are a total of `2*9 = 18` characters to
  decode.
* Left position = 'M' (ASCII = 77).  Relative to 'R' (ASCII = 82), this is `-5`
* Right position = 'W' (ASCII = 87).  Relative to 'R' = `+5`
* First coordinate is "OM" = (-3,-5)
* Second coordinate is "OV" = (-3,4)
* Raise the pen " R"
* Move to "UM" = (3,-5)
* Draw to "UV" = (3,4)
* Raise the pen " R"
* Move to "OQ" = (-3,-1)
* Draw to "UQ" = (3,-1)


This glyph string can be converted to a data.frame (using `hershey::convert_glyph_to_df()`) and plotted with [ggplot](https://cran.r-project.org/package=ggplot2).

```{r technical_h, fig.width=4, out.width="50%"}
glyph    <- '    8  9MWOMOV RUMUV ROQUQ'
glyph_df <- hershey::convert_glyph_to_df(glyph)

glyph_df

ggplot(glyph_df, aes(x, y, group = stroke)) + 
  geom_point() + 
  geom_path() + 
  coord_equal() + 
  theme_minimal() + 
  scale_x_continuous(breaks = scales::pretty_breaks()) + 
  scale_y_continuous(breaks = scales::pretty_breaks())

```
